$\pi$ with leftovers: \\ a mechanisation in Agda

### 2021-01-11 paper/paper.tex
Move acknowledgments to the end

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{
  $\pi$ with leftovers: \\ a mechanisation in Agda
  \thanks{
    The authors would also like to thank the anonymous referees for their valuable comments and helpful suggestions.
    We further want to thank Erika Kreuter, Wen Kokke, James Wood, Guillaume Allais, Bob Atkey, and Conor McBride for their work and thoughts.
    This work is supported by the UK EPSRC grant EP/K034413/1 ``From Data Types to Session Types: A Basis for Concurrency and Distribution'' (ABCD), and by the EU HORIZON 2020 MSCA RISE project 778233 ``Behavioural Application Program Interfaces'' (BehAPI).}
}
\titlerunning{$\pi$ with leftovers: a mechanisation in Agda}
\author{
  Uma Zalakain\inst{1}\orcidID{0000-0002-3268-9338}
  \and
  Ornela Dardha\inst{2}\orcidID{0000-0001-9927-7875}
}
\institute{
  University of Glasgow, Scotland \\ \email{u.zalakain.1@research.gla.ac.uk}
  \and
  University of Glasgow, Scotland \\ \email{ornela.dardha@glasgow.ac.uk}
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{$\pi$ with leftovers: \\ a mechanisation in Agda}
\titlerunning{$\pi$ with leftovers: a mechanisation in Agda}
\author{
  Uma Zalakain\inst{1}\orcidID{0000-0002-3268-9338}
  \and
  Ornela Dardha\inst{2}\orcidID{0000-0001-9927-7875}
}
\institute{
  University of Glasgow, Scotland \\ \email{u.zalakain.1@research.gla.ac.uk}
  \and
  University of Glasgow, Scotland \\ \email{ornela.dardha@glasgow.ac.uk}
}
% Support
% This work is supported by the UK EPSRC grant EP/K034413/1 ``From Data Types to Session Types: A Basis for Concurrency and Distribution'' (ABCD), and by the EU HORIZON 2020 MSCA RISE project 778233 ``Behavioural Application Program Interfaces'' (BehAPI).}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
\section*{Acknowledgments}

We further want to thank Erika Kreuter, Wen Kokke, James Wood, Guillaume Allais, Bob Atkey, and Conor McBride for their work and thoughts.
